Modi normali di oscillazione del Sole (Presentazione)

### 2017-06-17 MSS.tex
mf

\begin{frame}{Fattore astrofisico}

@@

\node (pep) at ($(s.south)+(47mm,-6mm)$) {\parbox{\textwidth}{\begin{equation*}\begin{split}\scriptscriptstyle II: R(p\Pelectron p)=&\scriptscriptstyle1.102(1\pm0.01)10^{-4}\midfrac{\rho}{\mu_e}T_6\expy{-1/2}\\
&\scriptscriptstyle[1+0.002(T_6-16)]R(pp)\end{split}\end{equation*}}};
\node[below=0.1mm of pep] (ec) {\parbox{\textwidth}{\begin{equation*}\begin{split}\scriptscriptstyle I: R(\cel{Be}{7}{}{}(\Pelectron,\Pnue)\cel{Li}{7}{}{})=&\scriptscriptstyle5.6(1\pm0.02)10^{-9}\midfrac{\rho}{\mu_e}T_6\expy{-1/2}\\
&\scriptscriptstyle[1+0.004(T_6-16)]\si{\per\second}\end{split}\end{equation*}}};

>>>>

\begin{frame}{Fattore astrofisico}
\centering
\begin{tikzpicture}[ampersand replacement=\&]

@@

\node (pep) at ($(s.south)+(47mm,-6mm)$) {\parbox{\textwidth}{\begin{equation*}\scriptscriptstyle II: R(p\Pelectron p)=\scriptscriptstyle1.102(1\pm0.01)10^{-4}\midfrac{\rho}{\mu_e}T_6\expy{-1/2}
\scriptscriptstyle[1+0.002(T_6-16)]R(pp)\end{equation*}}};
\node[below=0.1mm of pep] (ec) {\parbox{\textwidth}{\begin{equation*}\scriptscriptstyle I: R(\cel{Be}{7}{}{}(\Pelectron,\Pnue)\cel{Li}{7}{}{})=\scriptscriptstyle5.6(1\pm0.02)10^{-9}\midfrac{\rho}{\mu_e}T_6\expy{-1/2}\scriptscriptstyle[1+0.004(T_6-16)]\si{\per\second}\end{equation*}}};
